Missing the Point: Convergence of Multiple Imputation by Chained Equations Algorithms

### 2020-03-30 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Plots with patchwork package instead of ggarrange
Ran sim to show Gerko new plots (mean, var, est, pred).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

```{r}
# plot results
load("../Results/results.Rdata")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("../Results/results.Rdata")
source("../2.CreateFigures.R")

@@

What to evaluate?

- bias in regression coefficients

- bias in $R^2$ (= coefficient of determination)

-

@@

```{r, echo=FALSE, fig.cap="Convergence diagnostics (means)"}
bias_means_plot + R_means_plot + AC_means_plot + plot_layout(nrow = 3, guides = "collect")
```

```{r, echo=FALSE, fig.cap="Convergence diagnostics (variances)"}
bias_sds_plot + R_sds_plot + AC_sds_plot + plot_layout(nrow = 3, guides = "collect")
```

```{r, echo=FALSE, fig.cap="Convergence diagnostics (regression coefficients)"}
bias_ests_plot + bias_R_sq_plot + cov_plot + plot_layout(nrow = 3, guides = "collect")
```
